### 2021-07-12 src/paper/results/rapid_tests_statistics.tex
Add parameter notation where possible and fix typos.

In order to make most use out of limited data sources on rapid test usage, we model the
number of performed rapid tests as a result of time invariant willingness to do rapid
tests and time varying supply side factors and events that trigger rapid tests. Thus,
the parameters described in Section~\ref{subsec:rapid_test_demand} are only indirectly
related to the number of rapid tests that are actually performed in the model. When it
comes to positive and negative rapid tests, there is even an additional layer because
rapid tests imperfectly sensitive and specific.

@@

Such a large effect of rapid tests seems to be at odds with the general perception that
they are not very reliable. However, this is not the case, which can be seen from the
number of
false negative tests. At its peak at the beginning of May, there are more than 80 false
negative rapid tests per million inhabitants per day. While this number might sound low
in isolation, it becomes quite large when set in context: We estimate that at at the
the same time only 200 cases per million are detected by rapid tests. This means that
even at the time where discovery of cases via rapid tests is at its peak, almost
30\% of of people who are infected and make a test are not discovered by the test.

>>>>

In order to make most use out of limited data sources on rapid test usage, we model the
number of performed rapid tests as a result of time invariant willingness to do rapid
tests and time varying supply side factors and events that trigger rapid tests. Thus, the
$\pi$ parameters governing when individuals do rapid tests described in
Section~\ref{subsec:rapid_test_demand} are only indirectly related to the number of rapid
tests that are actually performed in the model. When it comes to positive and negative
rapid tests, there is even an additional layer because rapid tests are imperfectly
sensitive and specific.

@@

Such a large effect of rapid tests seems to be at odds with the general perception that
they are not very reliable. However, this is not the case, which can be seen from the
number of
false negative tests. At its peak at the beginning of May, there are more than 80 false
negative rapid tests per million inhabitants per day. While this number might sound low
in isolation, it becomes quite large when set in context: We estimate that at at the
the same time only 200 cases per million are detected by rapid tests. This means that
even at the time where discovery of cases via rapid tests is at its peak, almost
30\% of people who are infected and make a test are not discovered by the test.

### 2021-07-12 src/paper/results/share_known_cases.tex
Add parameter notation where possible and fix typos.

In 2020 the share of detected cases is much higher in older age groups as they are much
more likely to develop symptoms and symptomatic individuals are much more likely to be
tested. Starting in 2021 the share of detected cases not only depends on the overall
share of detected cases we feed into our model but also on the number of performed rapid
tests. As more and more (often asymptomatic and presymptomatic) individuals receive
positive rapid tests and receive confirmation, the share of detected cases starts to
increase, especially after March when rapid tests became much more widely available. This
effect is very visible for school pupils, (5-14, green line). As twice weekly rapid tests
become mandatory in schools and students start going to school after the Easter break,
the share of detected cases for that group increases drastically from 25\% to over 60\%
between April and June.

\begin{figure}[ht]
  \centering
  \includegraphics[width=0.5\textwidth]{figures/results/figures/share_known_cases/full_combined_baseline_by_age_group_rki}
  \caption{Share of Detected Cases by Age Group}
  \label{fig:share_known_cases_by_age_group}
  \floatfoot{\noindent \textit{Note:} The figure shows the share of cases that is
  reported as an official case via PCR confirmation for each age group in our population.
  We use the overall share of detected cases that was estimated through the case fatality
  ratio by \citet{Dunkelzifferradar2020} for all of 2020 and then assume it to be
  constant as vaccinations of the elderly strongly affect the case fatality rate which
  the project does not account for. To get from an overall share of detected cases to the
  share of cases that is detected in each age group we use that asymptomatic cases are
  much less likely to be detected. As our model covers age specific asymptomatic rates
  this endogenously leads to group specific share of detected cases that suggest that
  infections in younger age groups are under-detected. Starting in 2021 in addition to
  the overall numbers of detected cases through symptoms and the share of detected cases,
  cases are also detected through confirmation of positive rapid tests. This leads to an
  increase in the share of detected cases for all age groups but in particular for the
  younger age groups that are covered extensively with rapid tests through the rapid test
  requirement for participating in school. Age groups that have a high share of workers
  also disproportionately increase their detection rate.}
\end{figure}

>>>>

In 2020 the share of detected cases is much higher in older age groups as they are much
more likely to develop symptoms and symptomatic individuals are much more likely to be
tested. Starting in 2021 the share of detected cases not only depends on the overall
share of detected cases ($\psi_t$) we feed into our model but also on the number of
performed rapid tests (governed by the $\pi$ parameters). As more and more (often
asymptomatic and presymptomatic) individuals receive positive rapid tests and seek and
get confirming PCR tests, the share of detected cases starts to increase, especially
after March when rapid tests became much more widely available. This effect is very
visible for school pupils (5-14, green line). As twice weekly rapid tests become
mandatory in schools and students start going to school after the Easter break, the share
of detected cases for that group increases drastically from 25\% to over 60\% between
April and June.

\begin{figure}[ht]
  \centering
  \includegraphics[width=0.5\textwidth]{figures/results/figures/share_known_cases/full_combined_baseline_by_age_group_rki}
  \caption{Share of Detected Cases by Age Group}
  \label{fig:share_known_cases_by_age_group}
  \floatfoot{\noindent \textit{Note:} The figure shows the share of cases that is
  reported as an official case via PCR confirmation for each age group in our population.
  We use the overall share of detected cases ($\psi_t$) that was estimated through the
  case fatality ratio by \citet{Dunkelzifferradar2020} for all of 2020 and then assume it
  to be constant as vaccinations of the elderly strongly affect the case fatality rate
  which the project does not account for. To get from an overall share of detected cases
  to the share of cases that is detected in each age group we use that asymptomatic cases
  are much less likely to be detected. As our model covers age specific asymptomatic
  rates this endogenously leads to group specific share of detected cases that suggest
  that infections in younger age groups are under-detected. Starting in 2021 in addition
  to the overall numbers of detected cases through $\psi_t$, cases are also detected
  through confirmation of positive rapid tests. This leads to an increase in the share of
  detected cases for all age groups but in particular for the younger age groups that are
  covered extensively with rapid tests through the rapid test requirement for
  participating in school. Age groups that have high shares of workers also have
  disproportionately increases in their detection rates.}
\end{figure}

### 2021-07-12 src/paper/results/validation.tex
Fix figure references.
Rewrite section on rapid test statistics.
Add parameter notation where possible and fix typos.

Achieving a good in-sample fit does not necessarily guarantee that our model will also
be able to make out of sample predictions. For example, it could be that the results
are very sensitive to the exact number of vaccinations, the work mobility multiplier
or the number of rapid tests that are performed -- all of which are things that cannot
be exactly known ex-ante.

@@

For the out of sample predictions we predict the number of vaccinations between March
and June with a simple linear regression model that was fitted on vaccine data from
February. This prediction model is pessimistic compared to the actual number of
vaccinations. The work mobility multiplier is predicted to be constant at a value of
0.75, which is an approximate average of the second half of February. This turned out
to be optimistic.

The area that is fraught with the most uncertainty is the introduction of rapid test,
because it comprises both supply and demand factors. Moreover, accurately predicting
the number of rapid tests is expected to be important because rapid tests play a large
role for the transmission dynamic.

We therefore make a scenario analysis with different assumptions on the availability
of rapid tests. The number of rapid tests performed in each scenario can be seen in
Figure~\ref{fig:robustness_check_rapid_test_params}. All scenarios are the same
unti March 1 and have the same level of rapid tests when all supply constraints are
resolved. They differ in the date at which the full number of tests is reached. For
students and teachers the full number of rapid tests is reached after the easter
holidays. For rapid tests in the workplace and private rapid tests it is reached between
May 1 and June 10, depending on the scenario.

@@

  \floatfoot{\noindent \textit{Note:} Number of rapid tests performed in the different
  prediction scenarios. All scenarios are the same
  unti March 1 and have the same level of rapid tests when all supply constraints are
  resolved. They differ in the date at which the full number of tests is reached. For
  students and teachers the full number of rapid tests is reached after the easter
  holidays. For rapid tests in the workplace and private rapid tests it is reached
  between May 1 and June 10, depending on the scenario.
  }
\end{figure}

Moreover, the out of sample predictions assume that the share of detected cases that
would have obtained without rapid tests is not affected by the easter holidays because
the extent to which this was the case was estimated from case numbers in April.

The results of the out of sample prediction are displayed in
Figure~\ref{robustness_check_detailed}. While all scenarios considerably deviate from
the ex-post scenario, they all reproduce the steep increase of cases until the end
of April, followed by a decline until June. We can therefore conclude that our main
results are not sensitive to measurement errors in the number of rapid tests,
vaccinations or mobility data.

\begin{figure}[ht] % Robustness Check
  \centering
  \begin{subfigure}[b]{.425\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/results/figures/scenario_comparisons/robustness_check/full_new_known_case}
    \caption{Reported Cases}
    \label{fig:robustness_check_new_known_case}
  \end{subfigure}%
  \hfill
  \begin{subfigure}[b]{.425\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/results/figures/scenario_comparisons/robustness_check/full_newly_infected}
    \caption{Total Cases}
    \label{fig:robustness_check_newly_infected}
  \end{subfigure}
  \caption{Out of Sample Prediction for Reported and Total Cases from March to June
  2021.}
  \label{fig:robustness_check_detailed}
  \floatfoot{\noindent \textit{Note:} The ex-post scenario is an in-sample prediction
  that uses all available information and is very close to actual case numbers. For the
  other scenarios data on vaccinations, work mobility and rapid tests that became
  available after March 1 have been replaced by prediction models that are calibrated
  with data from February. Moreover, they do not model a lower number of detected cases
  over the easter holidays. The different scenarios make different assumptions on the
  date at which full availability of rapid tests is reached. While the out of sample
  predictions differ substantially for the exact case numbers at the beginning of June
  (between 20 and 70 cases per million), they can all reproduce the decline in case
  numbers that is jointly driven by seasonality, large scale rapid tests and
  vaccinations.}
\end{figure}

>>>>

Achieving a good in-sample fit does not necessarily guarantee that our model will also be
able to make out of sample predictions. For example, it could be that the results are
very sensitive to the exact number of vaccinations, the work mobility multiplier
($\rho_{w,\:attend,\:t}$) or the number of rapid tests (governed by the $\pi$ parameters)
that are performed -- all of which are things that cannot be exactly known ex-ante.

@@

For the out of sample predictions we predict the number of vaccinations between March and
June with a simple linear regression model that was fitted on vaccine data from February.
This prediction model is pessimistic compared to the actual number of vaccinations. The
work mobility multiplier ($\rho_{w,\:attend,\:t}$) is predicted to be constant at a value
of 0.75, which is an approximate average of the second half of February. This turned out
to be optimistic.

The area that is fraught with the most uncertainty is the introduction of rapid tests,
because it comprises both supply and demand factors. Moreover, accurately predicting the
number of rapid tests is expected to be important because rapid tests play a large role
for the transmission dynamic.

We therefore make a scenario analysis with different assumptions on the availability of
rapid tests. The number of rapid tests performed in each scenario can be seen in
Figure~\ref{fig:robustness_check_rapid_test_params}. All scenarios are the same until
March 1 and have the same level of rapid tests when all supply constraints are resolved.
They differ in the date at which the full number of tests is reached. For students
($\pi_{students,\:t}$) and teachers ($\pi_{teacher,\:t}$) the full number of rapid tests
is reached after the Easter holidays in all scenarios. For rapid tests in the workplace
($\pi_{w,\:s,\:t}$) and private rapid tests ($\pi_{private,\:t}$) it is reached between
May 1 and June 10, depending on the scenario.

@@

  \floatfoot{\noindent \textit{Note:} Number of rapid tests performed in the different
  prediction scenarios. All scenarios are the same until March 1 and have the same level
  of rapid tests when all supply constraints are resolved. They differ in the date at
  which the full number of tests is reached. For students ($\pi_{students,\:t}$) and
  teachers ($\pi_{teacher,\:t}$) the full number of rapid tests is reached after the
  Easter holidays in all scenarios. For rapid tests in the workplace ($\pi_{w,\:s,\:t}$)
  and private rapid tests ($\pi_{private,\:t}$) it is reached between May 1 and June 10,
  depending on the scenario. }
\end{figure}

Moreover, the out of sample predictions assume that the share of detected cases
($\psi_t$) that would have been obtained without rapid tests is not affected by the
Easter holidays because the extent to which this was the case was estimated from case
numbers in April.

The results of the out of sample prediction are displayed in
Figure~\ref{fig:robustness_check_detailed}. While all scenarios considerably deviate from
the ex-post scenario, they all reproduce the steep increase of cases until the end of
April, followed by a decline until June. We can therefore conclude that our main results
are not sensitive to measurement errors in the number of rapid tests, vaccinations or
mobility data.

\begin{figure}[ht] % Robustness Check
  \centering
  \begin{subfigure}[b]{.425\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/results/figures/scenario_comparisons/robustness_check/full_new_known_case}
    \caption{Reported Cases}
    \label{fig:robustness_check_new_known_case}
  \end{subfigure}%
  \hfill
  \begin{subfigure}[b]{.425\textwidth}
    \centering
    \includegraphics[width=\textwidth]{figures/results/figures/scenario_comparisons/robustness_check/full_newly_infected}
    \caption{Total Cases}
    \label{fig:robustness_check_newly_infected}
  \end{subfigure}
  \caption{Out of Sample Prediction for Reported and Total Cases from March to June
  2021.}
  \label{fig:robustness_check_detailed}
  \floatfoot{\noindent \textit{Note:} The ex-post scenario is an in-sample prediction
  that uses all available information and is very close to actual case numbers. For the
  other scenarios data on vaccinations, work mobility and rapid tests that became
  available after March 1 have been replaced by prediction models that are calibrated
  with data from February. Moreover, they do not model a lower number of detected cases
  over the Easter holidays. The different scenarios make different assumptions on the
  date at which full availability of rapid tests is reached. While the out of sample
  predictions differ substantially for the exact case numbers at the beginning of June
  (between 20 and 70 cases per million), they can all reproduce the decline in case
  numbers that is jointly driven by seasonality, large scale rapid tests and
  vaccinations.}
\end{figure}

\FloatBarrier
